---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **R Basics Exercise**

**Author**: Suchanya Namwong

------------------------------------------------------------------------

We will test on a few topics:

-   Basic Data Types

-   Basic Arithmetic

-   Vector

-   Vector Operations

-   Comparison operators

-   Vector Selection and Indexing

This is more of a review to make sure I've understood everything so far!

------------------------------------------------------------------------

**Solve the following problems using R**

**What is two to the power of five?**

```{r}
2^5
```

------------------------------------------------------------------------

**Create a vector called `stock.prices` with the following data points: 23,27,23,21,34**

```{r}
stock.prices <- c(23,27,23,21,34)
stock.prices
```

------------------------------------------------------------------------

**Assign names to the price data points relating to the day of the week, starting with Mon, Tue, Wed, etc...**

```{r}
names(stock.prices) <- c('Mon','Tue','Wed','Thu','Fri')
stock.prices
```

------------------------------------------------------------------------

**What was the average (mean) stock price for the week?**

```{r}
mean(stock.prices)
```

------------------------------------------------------------------------

**Create a vector called `over.23` consisting of logicals that correspond to the days where the stock price was more than \$23**

```{r}
over.23 <- stock.prices[stock.prices>23]
```

------------------------------------------------------------------------

**Use the `over.23` vector to filter out the stock.prices vector and only return the day and prices where the price was over \$23**

```{r}
over.23
```

------------------------------------------------------------------------

**Use a built-in function to find the day the price was the highest**

```{r}
stock.prices[stock.prices == max(stock.prices)]
```

------------------------------------------------------------------------
